---
title: "p8105_hw1_xg2489"
output: github_document
---
```{r}
library(tidyverse)
#load library for future use
```

```{r}
data("penguins", package = "palmerpenguins")
```

This dataset contains 8 variables including species, island, bill length(mm), bill depth(mm), flipper length(mm), body mass(g), sex and year. 
The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)` mm.


```{r warning=FALSE}

plot_df = 
  tibble(
    x = pull(penguins, bill_length_mm),
    y = pull(penguins, flipper_length_mm),
    color = pull(penguins, species)
  )
#use "pull" to choose specific variable
ggplot(plot_df, aes(x = x, y = y, color = color)) + geom_point()
#"geom_point()" is used to make scatter plot
ggsave("flipper_bill_scatterplot.png")
```

```{r warning=FALSE}

df = 
  tibble(
    sample  = rnorm(10),                      
    logic = sample > 0,                        
    chara   = rep(c("aa", "bb", "cc"), length.out = 10),                   
    factor   = factor(rep(c("low", "medium", "high"), length.out = 10))  
    )

sample_mean = mean(pull(df, sample))
logic_mean = mean(pull(df, logic))
chara_mean = mean(pull(df, chara))
factor_mean = mean(pull(df, factor))
sample_mean
logic_mean
chara_mean
factor_mean
```

When taking the mean of each variable, it works for numeric vectors and logical vectors but returns "NA" in character vector and factor vector.


