---
title: "p8105_hw1_xg2489"
output: github_document
---
```{r}
library(tidyverse)
#load library for future use
```

```{r}
data("penguins", package = "palmerpenguins")
```

This dataset contains 8 variables including species (Adelie, Chinstrap and Gentoo), island, bill length(mm), bill depth(mm), flipper length(mm), body mass(g), sex and year. 
The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)` mm.


```{r}

plot_df = 
  tibble(
    x = pull(penguins, bill_length_mm),
    y = pull(penguins, flipper_length_mm),
    color = pull(penguins, species)
  )
#use "pull" to choose specific variable
ggplot(plot_df, aes(x = x, y = y, color = color)) + geom_point()
#"geom_point()" is used to make scatter plot
ggsave("flipper_bill_scatterplot.png")
```

```{r}

df = 
  tibble(
    sample  = rnorm(10),                      
    logic = sample > 0,                        
    chara   = rep(c("aa", "bb", "cc"), length.out = 10),                   
    factor   = factor(rep(c("low", "medium", "high"), length.out = 10))  
    )
# use "rep()" to generate repeated elements for the vector. "length,out" set the vector length to be 10.
sample_mean = mean(pull(df, sample))
logic_mean = mean(pull(df, logic))
chara_mean = mean(pull(df, chara))
factor_mean = mean(pull(df, factor))
sample_mean
logic_mean
chara_mean
factor_mean
```

When taking the mean of each variable, it works for numeric vectors and logical vectors but returns "NA" in character vector and factor vector. For logical vectors, R treats "TRUE" and "FALSE" as "1" and "0" so their mean can be calculated.

```{r, eval = FALSE}
as.numeric(pull(df, logic))
as.numeric(pull(df, chara))
as.numeric(pull(df, factor))
```


When logic vector transforms to numeric vector, it converts "TRUE" to 1 and "FALSE" to 0 so it shows no "NA".

When character vector transforms to numeric vector, it converts everything to "NA" as strings do not have a numerical meaning.

When factor vector transforms to numeric vector, it converts "low","medium","high" to integers to show different factor levels so it also shows no "NA".

"as.numeric" explains "mean()" behaviors. Logical vector coerces to 1 and 0, making "mean()" works successfully. Character vector turns "NA" causing "mean()" to fail. Factor vector returns internal integer levels while "mean()" still fails because the gap between different categories is unspecified so the mean of categories is statistically meaningless.


